All Equal in the Presence of Death? A Quantitative Analysis of the Early Iron Age Cemeteries of Knossos, Crete

### 2021-06-22 README.Rmd
Readme changes

```{r Title, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below. 
Title <- "Family Fortunes: A Quantitative Analysis of the Early Iron Age Cemeteries of Knossos"
```

@@

This repository contains the data and code for the paper:

> Pollard, Dominic (2021). _`r Title`_. Name of journal/book, <https://doi.org/xxx/xxx>

The pre-print available is online here:

> Pollard, Dominic (2021). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### Repository contents

All data, text and code to recreate the paper and analysis therein are found in the 'analysis' folder. Within this, 'analysis/data' contains all raw and derived data, in .csv format. All charts and images from the paper can be found in 'analysis/figures', while the paper itself, and the BibTex file containing all cited works are found in 'analysis/paper'. The folder 'analysis/templates' contains the citation style file, and a template file used to set the style for the Word document produced by 'Family_Fortunes_Article.Rmd'.

@@

> Pollard, Dominic (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

The compendium is also available from figshare at: https://doi.org/10.6084/m9.figshare.13019588.v1

>>>>

```{r Title, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below. 
Title <- "All Equal in the Presence of Death? A Quantitative Analysis of the Early Iron Age Cemeteries of Knossos"
```

@@

This compendium contains the data and code for the paper:

> Pollard, Dominic (2021). _`r Title`_. Journal of Anthropological Archaeology, 63, 101320. <https://doi.org/10.1016/j.jaa.2021.101320>

### Compendium contents

This compendium consists of the raw data, full R code and text, and bibliographic information used in the creation of the article 'All Equal in the Presence of Death? A Quantitative Analysis of the Early Iron Age Cemeteries at Knossos, Crete'. This article provides a novel study of two large mortuary assemblages of the Cretan Early Iron Age, which have never been systematically compared through quantitative analysis. As part of the author's commitment to data sharing and maximal reproducibility, this compendium makes available all associated data and materials utilised in the production of the article.

The data pertain to the Knossos North and Fortetsa cemeteries, as presented in their respective publications (Brock 1957; Coldstream and Catling 1996). This compendium includes three related databases. The first contains entries for each individual ceramic vessel. Variables include the tomb, the vessel shape, its surviving dimensions, its ceramic period and corresponding absolute dating measures. In addition, all imports, ‘Oriental’ imitations, and antique (that is, Bronze Age) artefacts are identified. In total, this database comprises just over 4540 individual artefacts.

The second is similar, but with each entry corresponding to a find other than a ceramic vessel. A ‘material’ variable was added as these finds were not all made of the same substance. This database includes some 1620 individual artefacts.

The final database concerns the tombs themselves. Each tomb was accorded its own entry, with variables including dating (both relative and absolute), surviving dimensions, and the known and estimated number of interments, as well as tallies of the various artefact types recorded in the other two databases.

These data are utilised in the article, itself written in R, with all figures and tables generated on-the-fly through code. The full text and code, as well as the produced images, are stored in the compendium, as is all bibliographic information, in the form of a BibTex file which can be added to any reference manager.

This compendium allows the user to fully reproduce the analysis presented in the article, as well as to freely download and use the raw data for their own research. Further tombs in the wider Knossos area have since been added and are likewise made available in the compendium.

All data, text and code to recreate the paper and analysis therein are found in the 'analysis' folder. Within this, 'analysis/data' contains all raw and derived data, in .csv format. All charts and images from the paper can be found in 'analysis/figures', while the paper itself, and the BibTex file containing all cited works are found in 'analysis/paper'. The folder 'analysis/templates' contains the citation style file, and a template file used to set the style for the Word document produced by 'Knossos_Cemeteries_Article.Rmd'.

**References**:

>Brock, J.K. 1957. *Fortetsa: Early Greek Tombs Near Knossos*. Cambridge: Cambridge University Press.

>Coldstream, J. N., and H. W. Catling (eds.) 1996. *Knossos North Cemetery: Early Greek Tombs*. London: The British School at Athens Supplement 28. Vol. I-IV.

@@

> Pollard, Dominic (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for '`r Title`'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <http://doi.org/10.6084/m9.figshare.13019588>

@@

The compendium is also available from figshare at:

[![DOI](https://img.shields.io/badge/doi-10.6084/m9.figshare.13019588-blue.svg?style=flat&labelColor=whitesmoke&logo=data%3Aimage%2Fpng%3Bbase64%2CiVBORw0KGgoAAAANSUhEUgAAAB8AAAAfCAYAAAAfrhY5AAAJsklEQVR42qWXd1DTaRrHf%2BiB2Hdt5zhrAUKz4IKEYu9IGiGFFJJQ0gkJCAKiWFDWBRdFhCQUF3UVdeVcRQEBxUI3yY9iEnQHb3bdW1fPubnyz%2F11M7lvEHfOQee2ZOYzPyDv%2B3yf9%2Fk95YX4fx%2BltfUt08GcFEuPR4U9hDDZ%2FVngIlhb%2FSiI6InkTgLzgDcgfvtnovhH4BzoVlrbwr55QnhCtBW4QHXnFrZbPBaQoBh4%2FSYH2EnpBEtqcDMVzB93wA%2F8AFwa23XFGcc8CkT3mxz%2BfXWtq9T9IQlLIXYEuHojudb%2BCM7Hgdq8ydi%2FAHiBXyY%2BLjwFlAEnS6Jnar%2FvnQVhvdzasad0eKvWZKe8hvDB2ofLZ%2FZEcWsh%2BhyIuyO5Bxs2iZIE4nRv7NWAb0EO8AC%2FWPxjYAWuOEX2MSXZVgPxzmRL3xKz3ScGpx6p6QnOx4mDIFqO0w6Q4fEhO5IzwxlSwyD2FYHzwAW%2BAZ4fEsf74gCumykwNHskLM7taQxLYjjIyy8MUtraGhTWdkfhkFJqtvuVl%2F9l2ZquDfEyrH8B0W06nnpH3JtIyRGpH1iJ6SfxDIHjRXHJmdQjLpfHeN54gnfFx4W9QRnovx%2FN20aXZeTD2J84hn3%2BqoF2Tqr14VqTPUCIcP%2B5%2Fly4qC%2BUL3sYxSvNj1NwsVYPsWdMUfomsdkYm3Tj0nbV0N1wRKwFe1MgKACDIBdMAhPE%2FwicwNWxll8Ag40w%2BFfhibJkGHmutjYeQ8gVlaN%2BjO51nDysa9TwNUFMqaGbKdRJZFfOJSp6mkRKsv0rRIpEVWjAvyFkxNOEpwvcAVPfEe%2Bl8ojeNTx3nXLBcWRrYGxSRjDEk0VlpxYrbe1ZmaQ5xuT0u3r%2B2qe5j0J5uytiZPGsRL2Jm32AldpxPUNJ3jmmsN4x62z1cXrbedXBQf2yvIFCeZrtyicZZG2U2nrrBJzYorI2EXLrvTfCSB43s41PKEvbZDEfQby6L4JTj%2FfIwam%2B4%2BwucBu%2BDgNK05Nle1rSt9HvR%2FKPC4U6LTfvUIaip1mjIa8fPzykii23h2eanT57zQ7fsyYH5QjywwlooAUcAdOh5QumgTHx6aAO7%2FL52eaQNEShrxfhL6albEDmfhGflrsT4tps8gTHNOJbeDeBlt0WJWDHSgxs6cW6lQqyg1FpD5ZVDfhn1HYFF1y4Eiaqa18pQf3zzYMBhcanlBjYfgWNayAf%2FASOgklu8bmgD7hADrk4cRlOL7NSOewEcbqSmaivT33QuFdHXj5sdvjlN5yMDrAECmdgDWG2L8P%2BAKLs9ZLZ7dJda%2BB4Xl84t7QvnKfvpXJv9obz2KgK8dXyqISyV0sXGZ0U47hOA%2FAiigbEMECJxC9aoKp86re5O5prxOlHkcksutSQJzxZRlPZmrOKhsQBF5zEZKybUC0vVjG8PqOnhOq46qyDTDnj5gZBriWCk4DvXrudQnXQmnXblebhAC2cCB6zIbM4PYgGl0elPSgIf3iFEA21aLdHYLHUQuVkpgi02SxFdrG862Y8ymYGMvXDzUmiX8DS5vKZyZlGmsSgQqfLub5RyLNS4zfDiZc9Edzh%2FtCE%2BX8j9k%2FqWB071rcZyMImne1SLkL4GRw4UPHMV3jjwEYpPG5uW5fAEot0aTSJnsGAwHJi2nvF1Y5OIqWziVCQd5NT7t6Q8guOSpgS%2Fa1dSRn8JGGaCD3BPXDyQRG4Bqhu8XrgAp0yy8DMSvvyVXDgJcJTcr1wQ2BvFKf65jqhvmxXUuDpGBlRvV36XvGjQzLi8KAKT2lYOnmxQPGorURSV0NhyTIuIyqOmKTMhQ%2BieEsgOgpc4KBbfDM4B3SIgFljvfHF6cef7qpyLBXAiQcXvg5l3Iunp%2FWv4dH6qFziO%2BL9PbrimQ9RY6MQphEfGUpOmma7KkGzuS8sPUFnCtIYcKCaI9EXo4HlQLgGrBjbiK5EqMj2AKWt9QWcIFMtnVvQVDQV9lXJJqdPVtUQpbh6gCI2Ov1nvZts7yYdsnvRgxiWFOtNJcOMVLn1vgptVi6qrNiFOfEjHCDB3J%2BHDLqUB77YgQGwX%2Fb1eYna3hGKdlqJKIyiE4nSbV8VFgxmxR4b5mVkkeUhMgs5YTi4ja2XZ009xJRHdkfwMi%2BfocaancuO7h%2FMlcLOa0V%2FSw6Dq47CumRQAKhgbOP8t%2BMTjuxjJGhXCY6XpmDDFqWlVYbQ1aDJ5Cptdw4oLbf3Ck%2BdWkVP0LpH7s9XLPXI%2FQX8ws%2Bj2In63IcRvOOo%2BTTjiN%2BlssfRsanW%2B3REVKoavBOAPTXABW4AL7e4NygHdpAKBscmlDh9Jysp4wxbnUNna3L3xBvyE1jyrGIkUHaqQMuxhHElV6oj1picvgL1QEuS5PyZTEaivqh5vUCKJqOuIgPFGESns8kyFk7%2FDxyima3cYxi%2FYOQCj%2F%2B9Ms2Ll%2Bhn4FmKnl7JkGXQGDKDAz9rUGL1TIlBpuJr9Be2JjK6qPzyDg495UxXYF7JY1qKimw9jWjF0iV6DRIqE%2B%2FeWG0J2ofmZTk0mLYVd4GLiFCOoKR0Cg727tWq981InYynvCuKW43aXgEjofVbxIqrm0VL76zlH3gQzWP3R3Bv9oXxclrlO7VVtgBRpSP4hMFWJ8BrUSBCJXC07l40X4jWuvtc42ofNCxtlX2JH6bdeojXgTh5TxOBKEyY5wvBE%2BACh8BtOPNPkApjoxi5h%2B%2FFMQQNpWvZaMH7MKFu5Ax8HoCQdmGkJrtnOiLHwD3uS5y8%2F2xTSDrE%2F4PT1yqtt6vGe8ldMBVMEPd6KwqiYECHDlfbvzphcWP%2BJiZuL5swoWQYlS%2Br7Yu5mNUiGD2retxBi9fl6RDGn4Ti9B1oyYy%2BMP5G87D%2FCpRlvdnuy0PY6RC8BzTA40NXqckQ9TaOUDywkYsudxJzPgyDoAWn%2BB6nEFbaVxxC6UXjJiuDkW9TWq7uRBOJocky9iMfUhGpv%2FdQuVVIuGjYqACbXf8aa%2BPeYNIHZsM7l4s5gAQuUAzRUoT51hnH3EWofXf2vkD5HJJ33vwE%2FaEWp36GHr6GpMaH4AAPuqM5eabH%2FhfG9zcCz4nN6cPinuAw6IHwtvyB%2FdO1toZciBaPh25U0ducR2PI3Zl7mokyLWKkSnEDOg1x5fCsJE9EKhH7HwFNhWMGMS7%2BqxyYsbHHRUDUH4I%2FAheQY7wujJNnFUH4KdCju83riuQeHU9WEqNzjsJFuF%2FdTDAZ%2FK7%2F1WaAU%2BAWymT59pVMT4g2AxcwNa0XEBDdBDpAPvgDIH73R25teeuAF5ime2Ul0OUIiG4GpSAEJeYW9wDTf43wfwHgHLKJoPznkwAAAABJRU5ErkJggg%3D%3D)](http://doi.org/10.6084/m9.figshare.13019588)

### 2021-06-22 analysis/paper/Knossos_Cemeteries_Article.Rmd
Readme changes

Interest in the period grew in subsequent decades, as excavation at sites like the Toumba cemetery at Lefkandi in Euboea [@Desborough1970], and the North Cemetery at Knossos - discussed in this paper - yielded evidence for the maintenance of long-distance networks of exchange and interaction at the dawn of the EIA, as well as artefacts and rituals redolent of the Homeric epics [@Catling1995]. The growth of archaeological survey, with its broad chronological purview, began revealing long-term settlement dynamics in many regions, often transcending the traditional divides of the LBA, EIA and Classical era. Meanwhile a new generation of scholars in the 1980s and 1990s, particularly under the supervision of Snodgrass, pursued studies in burial practice, social organisation, the emergence of sanctuaries, and civic identities in the EIA [@Morgan1990; @Morgan2003; @Morris1987; @Whitley1991a]. All this work has culminated in the active rejection by many scholars of the appellation and interpretive baggage of the so-called ‘Dark Ages’ [see @Kotsonas2016; @Morris1997], and excavation and survey work pertaining to the EIA continue to grow apace [e.g. on Crete: @Haggis2016; @Zographaki2013].

>>>>

Interest in the period grew in subsequent decades, as excavation at sites like the Toumba cemetery at Lefkandi in Euboea [e.g. @Desborough1970], and the North Cemetery at Knossos - discussed in this paper - yielded evidence for the maintenance of long-distance networks of exchange and interaction at the dawn of the EIA, as well as artefacts and rituals redolent of the Homeric epics [@Catling1995]. The growth of archaeological survey, with its broad chronological purview, began revealing long-term settlement dynamics in many regions, often transcending the traditional divides of the LBA, EIA and Classical era. Meanwhile a new generation of scholars in the 1980s and 1990s, particularly under the supervision of Snodgrass, pursued studies in burial practice, social organisation, the emergence of sanctuaries, and civic identities in the EIA [@Morgan1990; @Morgan2003; @Morris1987; @Whitley1991a]. All this work has culminated in the active rejection by many scholars of the appellation and interpretive baggage of the so-called ‘Dark Ages’ [see @Kotsonas2016; @Morris1997], and excavation and survey work pertaining to the EIA continue to grow apace [e.g. on Crete: @Haggis2016; @Zographaki2013].
